---
title: "Capital 1"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(encoding = "utf-8")

```

#Capital 1 Online Case
 This is a group assignment for MKTG482. 
 Group member: Javier Urbina, Ahsan Kamran, Toshi Murakami
 
##Load data and library
```{r}

library(tidyverse)
library(mktg482)
library(nnet)
library(knitr)
library(janitor)
library(readxl)
library(psych)
library(statar)
library(mktg482)
library(tidyverse)
library(sjPlot)
library(AlgDesign)



rm(list=ls())
set.seed(13579)

```
First, we tranform the data and convert categorical variables into factors

```{r}
data1_count<- read_csv("Data1v2.csv")
data1_count<-data1_count%>% mutate(Fix_Var=factor(Fix_Var),APR=factor(APR), Annual_Fee=factor(Annual_Fee))

```
##Analyzing experimental data
```{r}

#We cannot choose Visa/Master Card so I ignored VISA_MC
lr.data1 <-glm(cbind(Sales,Fails)~APR*Fix_Var*Annual_Fee, data=data1_count, family=binomial)
summary(lr.data1)

```


##Now we will undertand how the difference in revenue

```{r}
data2<- read_csv("Data2.csv")
data2<-data2%>% mutate(Fix_Var=factor(Fix_Var),APR=factor(APR), Annual_Fee=factor(Annual_Fee),  `BK`=factor(`BK`))
LTV.reg <-lm(LTV ~ APR + Fix_Var+Annual_Fee + BK, data2)
LTV.reg

data2 <- data2 %>% mutate (pred_sales=predict(lr.data1, newdata=data2, type="response"), Expected_Revenue=pred_sales*LTV )
data2
data2%>%group_by(APR,Fix_Var, Annual_Fee)%>% summarise(mean(Expected_Revenue))
```

Knowing the expected revenue will help us determine who to send the mails. We have a strong incentive to test only a few variations given the aditional $1000 per variation tested and we also want to mail clients whose expected revenue is higher than the mailing cost of .5.


For example, for 



```{r}
##Generate Fractional Design
exp.design <- list(APR=c("14.9","16.8","19.8"),
                   Annual_Fee=c("0","20"),
                   Fix_Var=c("Fixed","Var."))
full.design <- expand.grid(exp.design)
full.design
frac.design <-optFederov(data=full.design, nTrials=5)
frac.design$design

```

##Analyzing experimental data-3
```{r}

data3 <- read_csv("Data3.csv")
data3<-data3%>% mutate(Fix_Var=factor(Fix_Var),APR=factor(APR), Annual_Fee=factor(Annual_Fee),  `BK`=factor(`BK`))
lr.data3 <-glm(cbind(Sales,Fails)~APR*Fix_Var*Annual_Fee*BK, data=data3, family=binomial)
summary(lr.data3)

```


##Now we will undertand how the difference in revenue based on the experiment we ran and results we got

```{r}
data2 <- data2 %>% mutate (pred_sales2=predict(lr.data3, newdata=data2, type="response"), Expected_Revenue2=pred_sales2*LTV )
data2
data2%>%group_by(APR,Fix_Var, Annual_Fee)%>% summarise(mean(Expected_Revenue2))
```
