---
title: "Capital 1"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(encoding = "utf-8")

```

#Intuit Online Case
 This is a group assignment for MKTG482. 
 Group member: Javier Urbina, Ahsan Kamran, Toshi Murakami
 
##Load data and library
```{r}

library(tidyverse)
library(mktg482)
library(nnet)
library(knitr)
library(janitor)
library(readxl)
library(psych)
library(statar)
library(mktg482)
library(tidyverse)
library(sjPlot)



rm(list=ls())
set.seed(13579)

```
First, we tranform the data and convert categorical variables into factors

```{r}
data1_count<- read_csv("Data1.csv")
data2<- read_csv("Data2.csv")

data1<-data1%>% mutate( `Fix/Var.`=factor(`Fix/Var.`), Date=factor(Date),APR=factor(APR), `Annual Fee`=factor(`Annual Fee`), `VISA/MC`=factor(`VISA/MC`), `BK`=factor(`BK`))

data1<-uncount(data1_count, `Accounts`)
```


##Split Data into test and training

```{r}

```




## Develop Model
```{r}
smobile_training_lr<-glm(churn~revenue+mou+overage+roam+changem+changer+dropvce+blckvce+unansvce+custcare+threeway+months+uniqsubs+phones+eqpdays+age+children+creditaa+refurb+occprof+occcler+occcrft+occstud+occhmkr+occret+occself+travel+retcalls+refer+incmiss+income+mcycle, family=binomial, data=smobile_training)

summary(smobile_training_lr)

#Adding Odds Rations
cbind(COEF=coef(smobile_training_lr),confint(smobile_training_lr))
exp(cbind(COEF=coef(smobile_training_lr),confint(smobile_training_lr)))

```

##Predictions
```{r}
smobile_training$lr_pred <- predict(smobile_training_lr,data= smobile_training, type="response")
smobile_test$lr_pred <- predict(smobile_training_lr, newdata=smobile_test,type="response")
rollout$lr_pred <- predict(smobile_training_lr, newdata=rollout,type="response")

```

## Checking Model Effectiveness
```{r}
gainsplot(smobile_test$lr_pred , label.var =smobile_test$churn)
gainsplot(smobile_training$lr_pred , label.var =smobile_training$churn)
```

## Plot Predictions
```{r}
plot_model(smobile_training_lr)
plot_model(smobile_training_lr,type="pred")
```

## Variable Importance
```{r}
varimp.logistic(smobile_training_lr)
```
## Variable Importance Chart
```{r}
varimp.logistic(smobile_training_lr) %>% plotimp.logistic()
# Important Variables [Vr imp >1.40] 
#1. Home-maker occupation 
#2. # of days of current equipment
#3. Crafts occupation
#4. Mean monthly minutes of use
#5. Age
#6. Mean # of blocked calls
#7. Months in service
```


Given this variables, we realize that we cant influence Ocupation or client parameters or behaviour, but we can target customers who have older equipment or have low months of use.
## Avg customer spend over lifetime
```{r}
smobile%>%
  group_by(churn) %>%
  summarise(mean_revenue=mean(revenue))
#Similar monthly spending for both categories
```

## Testing who to target
```{r}
rollouttgt<- rollout%>%
  mutate(eqpdays_ntile=ntile(eqpdays,5),mou_ntile=ntile(-mou,5))

rollouttgt %>%
  group_by(eqpdays_ntile) %>%
  summarise ( mean_pred=mean(lr_pred),mean_eqpdays=mean(eqpdays),mean_spending=mean(revenue), mean_minutes=mean(mou))

rollouttgt %>%
  group_by(mou_ntile) %>%
  summarise ( mean_pred=mean(lr_pred),mean_eqpdays=mean(eqpdays),mean_spending=mean(revenue), mean_minutes=mean(mou))


```


## Testing the effect of changing the equipment for the lowest n_tile (eqpdays=0)
```{r}
rollout_1 <-rollouttgt

rollout_1<-rollout_1 %>% mutate(eqpdays=ifelse(eqpdays_ntile==5,0,eqpdays))

rollout_1$test1<- predict(smobile_training_lr, newdata=rollout_1,type="response")

rollout_1%>% summarise(base=mean(lr_pred),test=mean(test1))

#We can test the churn only for the desired segment

rollout_1%>% filter(eqpdays_ntile==5)%>% summarise(base=mean(lr_pred),test=mean(test1))

#we can observe a steep decline in the churn chance in the specified segment

```


## Now, we can test the effect of changing the equipment for everyone
```{r}
rollout_1 <-rollouttgt

rollout_1<-rollout_1 %>% mutate(eqpdays=0)

rollout_1$test1<- predict(smobile_training_lr, newdata=rollout_1,type="response")

rollout_1%>% summarise(base=mean(lr_pred),test=mean(test1))
```



## Blocked voice
```{r}
rollout_1 <-rollouttgt

rollout_1<-rollout_1%>% mutate(blckvce_ntile=ntile(blckvce,5))

rollout_1<-rollout_1 %>% mutate(blckvce=ifelse(blckvce_ntile==5,blckvce/2,blckvce))

rollout_1$test1<- predict(smobile_training_lr, newdata=rollout_1,type="response")

rollout_1%>% summarise(base=mean(lr_pred),test=mean(test1))

rollout_1%>% filter(blckvce_ntile==5)%>% summarise(base=mean(lr_pred),test=mean(test1))
```

## Referals: Create a Campaign that incentivises people to send referalsa dn get their friends to join if they have not made a referal yet
```{r}
rollout_1 <-rollouttgt

rollout_1<-rollout_1 %>% mutate(testing=ifelse(refer==0,1,refer), refer=ifelse(refer==0,1,refer))

rollout_1$test1<- predict(smobile_training_lr, newdata=rollout_1,type="response")

rollout_1%>% summarise(base=mean(lr_pred),test=mean(test1))

rollout_1%>% filter(testing==1)%>% summarise(base=mean(lr_pred),test=mean(test1))
```