---
title: "Capital 1"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(encoding = "utf-8")

```

#Capital 1 Online Case
 This is a group assignment for MKTG482. 
 Group member: Javier Urbina, Ahsan Kamran, Toshi Murakami
 
##Load data and library
```{r}

library(tidyverse)
library(mktg482)
library(nnet)
library(knitr)
library(janitor)
library(readxl)
library(psych)
library(statar)
library(mktg482)
library(tidyverse)
library(sjPlot)
library(AlgDesign)



rm(list=ls())
set.seed(13579)

```
First, we tranform the data and convert categorical variables into factors

```{r}
data1_count<- read_csv("Data1v2.csv")


data1_count<-data1_count%>% mutate(Fix_Var=factor(Fix_Var),APR=factor(APR), Annual_Fee=factor(Annual_Fee))

```

```{r}
##Generate Fractional Design
exp.design <- list(APR=c("14.9","16.8","19.8"),
                   Annual_Fee=c("0","20"),
                   Fix_Var=c("Fixed","Var."))
full.design <- expand.grid(exp.design)
full.design
frac.design <-optFederov(data=full.design, nTrials=5)
frac.design$design
get.estimable.coefficients(full.design, frac.design)

```

##Analyzing experimental data
```{r}
lr.data1 <-glm(cbind(Sales,Fails)~APR*Fix_Var*Annual_Fee, data=data1_count, family=binomial)
summary(lr.data1)

#We cannot choose Visa/Master Card so I ignored VISA_MC
lr.data1 <-glm(cbind(Sales,Fails)~APR*Fix_Var*Annual_Fee*, data=data1_count, family=binomial)
summary(lr.data1)


```

## Adding results to full design
```{r}
full.design.results <- full.design %>%
  mutate(sales=c(0.051546825,0.038672537, 0.021859992,0.023508866, 0.010550595, 0.004584047, NA,NA,NA,0.01617592,NA,NA))
full.design.results

```

## Adding Predicted Reponses to Full Design
```{r}
full.design.results <- full.design.results %>%
mutate(pred = predict(lr.data1, newdata=full.design.results, type="response"),
pred_sales = 10000*pred)
full.design.results

```
##Now we will undertand how the difference in revenue

```{r}
data2<- read_csv("Data2.csv")
data2<-data2%>% mutate(Fix_Var=factor(Fix_Var),APR=factor(APR), Annual_Fee=factor(Annual_Fee),  `BK`=factor(`BK`))

LTV.reg <-lm(LTV ~ APR + Fix_Var+Annual_Fee + BK, data2)
LTV.reg

```

# Predicting probability of sale for each product type and BK level
```{r}
