---
title: "Intuit Online"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(encoding = "utf-8")

```

#Intuit Online Case
 This is a group assignment for MKTG482. 
 Group member: Javier Urbina, Arsan Kamran, Toshi Murakami
 
##Load data and library
```{r}
library(tidyverse)
library(mktg482)
library(nnet)

rm(list=ls())
set.seed(13579)
load("intuit_online.Rdata")
```


##Split Data into test and training

```{r}
intuit_training <- intuit %>% filter(training==1)
intuit_test<-intuit %>% filter(training==0)
```

##Neural Network 

```{r}
intuit_nn5 <- nnet(res~speeddown+speedup+last+numords+dollars+sincepurch+version2013+upgraded+payroll+bizflag+sex+income+medhvalue,data=intuit_training, size=5, decay=0.01, maxit=1000)

intuit_nn10 <- nnet(res~speeddown+speedup+last+numords+dollars+sincepurch+version2013+upgraded+payroll+bizflag+sex+income+medhvalue,data=intuit_training, size=10, decay=0.01, maxit=1000)

```


```{r}
pred_nn5_training<- predict(intuit_nn5,type="raw")
pred_nn5_test<- predict(intuit_nn5,newdata = intuit_test,type="raw")


pred_nn10_training<- predict(intuit_nn10,type="raw")
pred_nn10_test<- predict(intuit_nn10,newdata = intuit_test,type="raw")

```


##Logistic Regression

```{r}
intuit_lr<-glm(res~speeddown+speedup+last+numords+dollars+sincepurch+version2013+upgraded+payroll+bizflag+sex+income+medhvalue,family=binomial, data=intuit_training)

pred_lr_training<-predict(intuit_lr, type="response")
pred_lr_test<-predict(intuit_lr,newdata=intuit_test ,type="response")
```

##Model Performance comparison

```{r}
gainsplot(pred_nn5_test,pred_nn10_test,pred_lr_test, label.var =intuit_test$res )
gainsplot(pred_nn5_training,pred_nn10_training,pred_lr_training, label.var =intuit_training$res )
```

In each NN prediction works better than logistic regression, thus we decided to use NN model.
In NN models, 10 layer has more overfitting problem than 5 layer model. Thus we decided to use 5 layer model.

Assign NN result to Wave2 data.
```{r}
pred_nn5_wave2<- intuit.wave2 %>% 
  mutate(pred_wave2=predict(intuit_nn5,newdata = intuit.wave2,type="raw"))
```

##Calculate break even rate

 Cost/target : $1.60
 Target Profit : $5.6
 Break Even Response rate is described as 7.2/180 = 4%

```{r}
BER=7.2/180
BER
```

##Set target customers
For the customers in the dataset, create a new variable (call it ÅgtargetÅh) with a value of 1 if the customerÅfs predicted probability is greater than or equal to the breakeven response rate(4%) and 0 otherwise.
```{r}
options(encoding = "utf-8")

intuit.wave2<-pred_nn5_wave2 %>%
  mutate(target=1*(pred_wave2>= BER))
```


```{r}
intuit.wave2 %>% 
  group_by(target) %>% 
  summarise(num_target=n(), perc_target=num_target/25000, response_rate=mean(pred_wave2)) 
```

Of all the customer base, 32.7% of the customer are the target and response rate is 9.6%

##Profitability analysis for Logistic Regression
```{r}
intuit_wave2_res<- intuit.wave2%>% 
  filter(target==1) %>% 
  summarise(frac_mailed=n()/25000, resp_rate=mean(pred_wave2)) %>% 
  mutate(num_mailed=25000*frac_mailed,
         num_responded=resp_rate*num_mailed,
         profit=180*num_responded-1.6*num_mailed,
         ave_profit=profit/num_mailed)
intuit_wave2_res
```


So basically if we decide to send a email to all the customers who exceeds the break even rate of 4%, we get 9% response rate, and profit of $129,330(average profit of $15.7). We can lower the threashold(now it is 4%) and send broader customer base(our objective is to maximize profit not ROI).
