---
title: "Pentathlon (Part III)"      # Replace with name of assignment
author: 
   - name: Section 32        
   - name: Ahsan Kamran
   - name: Toshi Murakami
   - name: Javier Urbina     
output:
  html_notebook: default
---

# Preliminaries

### Determine notebook defaults:
```{r, include=FALSE}
knitr::opts_chunk$set(echo=TRUE,      # Print all the code in all the chunks
                      warning=FALSE,  # Don't print warning statements
                      message=FALSE,  # Don't print other R output messages
                      comment=NA)     # Helps produce prettier output
```

### Load packages:
```{r, echo=FALSE, message = FALSE, warning = FALSE}
library(gmodels)
library(modelr)
library(janitor)
library(haven)
library(readxl)
library(knitr)
library(psych)
library(statar)
library(tidyverse)
```

### Read in the data:
```{r}
load("PentathlonTargeting.Rdata")

pent <- pent %>% mutate(age=factor(age), female=factor(female), buyer=factor(buyer))

#Now we create the training and testing split

pent.train<- pent%>% filter(training==1)
pent.test<- pent%>% filter(training==0)
```

## Part 1 Analyising the different offers

Type your answer text here, intervowen with blocks of R code

```{r}
# First  we create a logistic regression model for every type of offer ( endurance, backcountry, etc)

lr.backcountry <- glm(buyer ~ age + female + income + education + children+ freq_endurance+freq_strength+freq_water+freq_team+freq_backcountry+freq_winter+freq_racquet,
family=binomial, data=pent.train %>% filter(message=="backcountry"))

pent.test <- pent.test %>%
mutate(pr.backcountry = predict(lr.backcountry, newdata=pent.test, type="response"))
```


And we repeat for every other message

```{r}
# Endurance

lr.endurance <- glm(buyer ~ age + female + income + education + children+ freq_endurance+freq_strength+freq_water+freq_team+freq_backcountry+freq_winter+freq_racquet,
family=binomial, data=pent.train %>% filter(message=="endurance"))

pent.test <- pent.test %>%
mutate(pr.endurance = predict(lr.endurance, newdata=pent.test, type="response"))
```



```{r}
# Strength

lr.strength <- glm(buyer ~ age + female + income + education + children+ freq_endurance+freq_strength+freq_water+freq_team+freq_backcountry+freq_winter+freq_racquet,
family=binomial, data=pent.train %>% filter(message=="strength"))

pent.test <- pent.test %>%
mutate(pr.strength = predict(lr.strength, newdata=pent.test, type="response"))
```

```{r}
#Water

lr.water <- glm(buyer ~ age + female + income + education + children+ freq_endurance+freq_strength+freq_water+freq_team+freq_backcountry+freq_winter+freq_racquet,
family=binomial, data=pent.train %>% filter(message=="water"))

pent.test <- pent.test %>%
mutate(pr.water = predict(lr.water, newdata=pent.test, type="response"))
```

```{r}
#Team

lr.team <- glm(buyer ~ age + female + income + education + children+ freq_endurance+freq_strength+freq_water+freq_team+freq_backcountry+freq_winter+freq_racquet,
family=binomial, data=pent.train %>% filter(message=="team"))

pent.test <- pent.test %>%
mutate(pr.team = predict(lr.team, newdata=pent.test, type="response"))
```

```{r}
#Winter

lr.winter <- glm(buyer ~ age + female + income + education + children+ freq_endurance+freq_strength+freq_water+freq_team+freq_backcountry+freq_winter+freq_racquet,
family=binomial, data=pent.train %>% filter(message=="winter"))

pent.test <- pent.test %>%
mutate(pr.winter = predict(lr.winter, newdata=pent.test, type="response"))
```

```{r}
#Racquet

lr.racquet <- glm(buyer ~ age + female + income + education + children+ freq_endurance+freq_strength+freq_water+freq_team+freq_backcountry+freq_winter+freq_racquet,
family=binomial, data=pent.train %>% filter(message=="racquet"))

pent.test <- pent.test %>%
mutate(pr.racquet = predict(lr.racquet, newdata=pent.test, type="response"))
```

## Question 2
```{r}

pent.test<- pent.test %>%
   mutate(pr.max = pmax(pr.backcountry, pr.endurance, pr.water, pr.team, pr.winter, pr.racquet,pr.strength),
          mail.offer=case_when(
             pr.backcountry==pr.max ~ "Backcountry",
             pr.endurance==pr.max~ "Endurance",
             pr.water==pr.max~ "Water",
             pr.team==pr.max ~ "Team",
             pr.winter==pr.max~ "Winter",
             pr.racquet==pr.max ~ "Racquet",
             pr.strength==pr.max~"Strength"))

pent.test%>% tabyl(mail.offer )


```

## Question 3

Type your answer text here, intervowen with blocks of R code


```{r}


pent.test %>% filter(buyer==1) %>% 
  group_by(message) %>% 
   summarise(avg_os_backcountry= mean(backcountry_os), 
             avg_os_endurance=mean(endurance_os), 
             avg_os_racquet=mean(racquet_os), 
             avg_os_team=mean(team_os),
             avg_os_water=mean(water_os),
             avg_os_winter=mean(winter_os),
             avg_os_strength=mean(strength_os),
             avg_os_sum=avg_os_strength+avg_os_winter+avg_os_water+avg_os_team+avg_os_racquet+avg_os_backcountry+avg_os_endurance,
             avg_total=mean(total_os))
#calculate bucket size for each of message. Bucket size for endurance 56.13240 / strength 56.46285 /team...


pent.test<- pent.test %>% 
  mutate(bucket_endurance=56.13240, 
         bucket_strength=56.46285,
         bucket_water=65.00817,
         bucket_team=60.43344,
         bucket_backcountry=61.62745, 
         bucket_winter=57.28686,
         bucket_racquet=57.58275)

pent.test <- pent.test %>%
  mutate(ep.backcountry=pr.backcountry*bucket_backcountry*0.4,
         ep.endurance=pr.endurance*bucket_endurance*0.4,
         ep.racquet=pr.racquet*bucket_racquet*0.4,
         ep.team=pr.team*bucket_team*0.4,
         ep.water=pr.water*bucket_water*0.4, 
         ep.winter=pr.winter*bucket_winter*0.4,
         ep.strength=pr.strength*bucket_strength*0.4)

pent.test<- pent.test %>%
   mutate(ep.max = pmax(ep.backcountry, ep.endurance, ep.water, ep.team, ep.winter, ep.racquet,ep.strength),
          mail.offer.ep=case_when(
             ep.backcountry==ep.max ~ "Backcountry",
             ep.endurance==ep.max~ "Endurance",
             ep.water==ep.max~ "Water",
             ep.team==ep.max ~ "Team",
             ep.winter==ep.max~ "Winter",
             ep.racquet==ep.max ~ "Racquet",
             ep.strength==ep.max~"Strength"))

pent.test%>% tabyl(mail.offer.ep )

```

##Q5. Using the predicted profit for all consumers in the test sample, what profit can we obtain on average per e-mailed customer when we customize the message to each customer?


```{r}
pent.test %>%
  group_by(mail.offer.ep) %>% 
  summarise(sum_ep=sum(ep.max), num=n(),avg_ep_customer=sum_ep/num)

pent.test %>% 
   summarise_at(vars(ep.max),list(mean))
```

For total 180,000 customers in test sample, average estimated profit will be 0.72.

##Q6. Using the predicted profit for all consumers in the test sample, what profit can Pentathlon obtain on average per e-mailed customer if every customer receives the same message? Answer the question for each of the seven possible message(endurance, strength, water, team, backcountry, winter, or racquet).

```{r}
pent.test %>% 
   summarise_at(vars(ep.backcountry, ep.endurance,ep.racquet,ep.team,ep.water,ep.winter, ep.strength, ep.max),list(mean))
```

If all the customers get the same message, most profitable one will be Water category. But estimated profit will be 0.66 euro/customer which is lower than our prediction in Q5(0.72/customer)

##Q7. Using the predicted profit for all consumers in the test sample, what profit can Pentathlon obtain on average per e-mailed customer if every customer is assigned at random to one of the seven messages?

```{r}
pent.test<- pent.test %>%
   mutate(pr.random=case_when(
             message=="backcountry" ~ pr.backcountry,
             message=="endurance"~ pr.endurance,
             message=="water"~pr.water,
             message=="team"~pr.team,
             message=="winter"~pr.winter,
             message=="racquet"~pr.racquet,
             message=="strength"~pr.strength))

pent.test <- pent.test %>%
  mutate(ep.random=case_when(
             message=="backcountry" ~ pr.random*bucket_backcountry*0.4,
             message=="endurance"~  pr.random*bucket_endurance*0.4,
             message=="water"~ pr.random*bucket_water*0.4,
             message=="team"~ pr.random*bucket_team*0.4,
             message=="winter"~ pr.random*bucket_winter*0.4,
             message=="racquet"~ pr.random*bucket_racquet*0.4,
             message=="strength"~ pr.random*bucket_strength*0.4))

pent.test %>% 
   summarise_at(vars(ep.random, ep.max),list(mean))

```

##Q8.what improvement (in percent and in total Euro) does Pentathlon expect to get from customizing the message to each customer rather than assigning customers a message at random?

 If we send email at random, we get 0.57euro/ customer total of 2.88M Euro from 5M customers. 
 But by targeting the customer we get 0.72euro/customer total of 3.60M Euro from 5M customers. 
 Targeting increases the profit by25% (0.72/0.57-1)
 
 
 ##Part 2. Comment on draft for new e-mail policy proposal
 
  
