---
title: "S Mobile"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(encoding = "utf-8")

```

#Intuit Online Case
 This is a group assignment for MKTG482. 
 Group member: Javier Urbina, Ahsan Kamran, Toshi Murakami
 
##Load data and library
```{r}
library(tidyverse)
library(mktg482)
library(nnet)

rm(list=ls())
set.seed(13579)
load("smobile_churn.Rdata")
```


##Split Data into test and training

```{r}
smobile_training <- smobile %>% filter(training==1)
smobile_test<-smobile %>% filter(training==0)
```

## Develop Model

```{r}
smobile_training_lr<-glm(churn~revenue+mou+overage+roam+changem+changer+dropvce+blckvce+unansvce+custcare+threeway+months+uniqsubs+phones+eqpdays+age+children+creditaa+refurb+occprof+occcler+occcrft+occstud+occhmkr+occret+occself+travel+retcalls+refer+incmiss+income+mcycle,family=binomial, data=smobile_training)

summary(smobile_training_lr)

#Adding Odds Rations
cbind(COEF=coef(smobile_training_lr),confint(smobile_training_lr))
exp(cbind(COEF=coef(smobile_training_lr),confint(smobile_training_lr)))

pred_lr_training<-predict(smobile_training_lr, type="response")
pred_lr_test<-predict(smobile_training_lr,newdata=smobile_test ,type="response")
```
##Predictions
```{r}
pred_lr_training <- predict(smobile_training_lr,type="response")
pred_lr_test <- predict(smobile_training_lr, newdata=smobile_test,type="response")
```

## Gains Plot
```{r}
<<<<<<< Updated upstream
gainsplot(pred_lr_test,label.var =smobile_test$res)
=======
#gainsplot(pred_lr_test,label.var =smobile_test$res)
---
title: "S Mobile"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(encoding = "utf-8")

```

#Intuit Online Case
 This is a group assignment for MKTG482. 
 Group member: Javier Urbina, Ahsan Kamran, Toshi Murakami
 
##Load data and library
```{r}
library(tidyverse)
library(mktg482)
library(nnet)

rm(list=ls())
set.seed(13579)
load("smobile_churn.Rdata")
```


##Split Data into test and training

```{r}
smobile_training <- smobile %>% filter(training==1)
smobile_test<-smobile %>% filter(training==0)
```

## Develop Model

```{r}
smobile_training_lr<-glm(churn~revenue+mou+overage+roam+changem+changer+dropvce+blckvce+unansvce+custcare+threeway+months+uniqsubs+phones+eqpdays+age+children+creditaa+refurb+occprof+occcler+occcrft+occstud+occhmkr+occret+occself+travel+retcalls+refer+incmiss+income+mcycle,family=binomial, data=smobile_training)

summary(smobile_training_lr)

#Adding Odds Rations
cbind(COEF=coef(smobile_training_lr),confint(smobile_training_lr))
exp(cbind(COEF=coef(smobile_training_lr),confint(smobile_training_lr)))

pred_lr_training<-predict(smobile_training_lr, type="response")
pred_lr_test<-predict(smobile_training_lr,newdata=smobile_test ,type="response")
```


##Predictions
```{r}
pred_lr_training <- predict(smobile_training_lr,type="response")
pred_lr_test <- predict(smobile_training_lr, newdata=smobile_test,type="response")
```

## Gains Plot
```{r}
gainsplot(pred_lr_test,label.var =smobile_test$res)
```
>>>>>>> Stashed changes
```